Verifying Fine-Grained and Lock-Free Binary Search Trees

### 2021-07-08 concurrency/intro.tex
trying to describe generic atomic specs

The binary search tree (BST) is a common implementation of an ordered
map, a widely used data structure. The concurrent version of the
ordered map forms the bedrock of many parallel programs. We formally
verified the functional correctness of two versions of fine-grained
concurrent binary search trees (CBST) written in C. One adopts the
hand-over-hand locking technique \cite{bayer1977}, the other is lock
free by using atomic primitives such as compare and swap (CAS). Both
CBST implementations support insert, lookup, and delete operations;
they also share the ``same'' specifications to some extent in our
verification. All the proof is machine-checked in Coq.

@@

Our specific contributions are:
\begin{itemize}
\item To the best of our knowledge, this is the first mechanized
verification of an concurrent search-based data structure written in a
real programming language.

>>>>

The binary search tree (BST) is a common implementation of an ordered
map, a widely used data structure. The concurrent version of the
ordered map forms the bedrock of many parallel programs. We formally
verified the functional correctness of two versions of fine-grained
concurrent binary search trees (CBST) written in C. One adopts the
hand-over-hand locking technique \cite{bayer1977}, the other is lock
free by using atomic primitives such as compare and swap (CAS). Both
CBST implementations support insert, lookup, and delete operations; %or do we have lock-free without delete?
they also share the ``same'' specifications to some extent in our
verification. All the proof is machine-checked in Coq. %Say something about existing proofs of fine-grained data structures and how we compare.

@@

Our specific contributions are:
\begin{itemize}
\item To the best of our knowledge, this is the first mechanized
verification of an concurrent search-based data structure written in a
real programming language. %should probably clarify what we mean by "real"
